`gosset`: An R package for analysis and synthesis of ranking data in agricultural experimentation

### 2022-06-22 inst/paper/paper.Rmd
Update paper.Rmd

---
title: '`gosset`: An R package for analysis and synthesis of ranking data in agricultural experimentation'
abstract: null
output:
   pdf_document:
     fig_caption: true
     number_sections: false
     keep_tex: false
latex_engine: pdflatex
#output:
# word_document: default
editor_options:
  markdown:
    wrap: 72
bibliography: paper.bib
csl: citationstyle.csl
header-includes:
  - \usepackage{pdfpages}
  - \usepackage{caption}
  - \usepackage{xcolor}
  - \captionsetup[figure]{font=small}
  - \captionsetup[table]{font=small}
---

>>>>

---
title: '`gosset`: An R package for analysis and synthesis of ranking data in agricultural experimentation'
abstract: null
output: 
   pdf_document:
     fig_caption: true
     number_sections: false
     keep_tex: false
latex_engine: pdflatex
#output:
# word_document: default
editor_options:
  markdown:
    wrap: 72
bibliography: paper.bib
csl: apa.csl
header-includes:
  - \usepackage{pdfpages}
  - \usepackage{caption}
  - \usepackage{xcolor}
  - \captionsetup[figure]{font=small}
  - \captionsetup[table]{font=small}
---
